
% \yd{zn: plz re-phrase some sentences if having time---too similar to abstract}
% \yd{zn: plz also add a small para to talk about two/three future points: such as pre-train ?}

In this paper, we propose the \model\ (\short) architecture for modeling Web-scale heterogeneous and dynamic graphs. 
To model heterogeneity, we use the meta relation $\langle \tau(s), \phi(e), \tau(t) \rangle$ to decompose the interaction and transform matrices, enabling the model to have the similar modeling capacity with fewer resources.
To capture graph dynamics, we present %the \dynamic\ model. 
%\dynamic\ %keeps the whole graph with each edge/node associated with its timestamp to avoid information loss, and then 
%leverages 
the relative temporal encoding  (RTE) technique to incorporate temporal information using limited computational resources. 
To conduct efficient and scalable training of \short\ on Web-scale data, we design the heterogeneous Mini-Batch graph sampling algorithm---\sampling. 
We conduct comprehensive experiments on the Open Academic Graph, and show that the proposed \short\ model can capture both heterogeneity and outperforms all the state-of-the-art GNN baselines on various downstream tasks.

In the future, we will explore whether \short\ is able to generate heterogeneous graphs, e.g., predict new papers and their titles, and whether we can pre-train \short\ to benefit tasks with scarce labels.


\vpara{Acknowledgements.} We would like to thank Xiaodong Liu for helpful discussions. This work is partially supported by NSF III-1705169, NSF CAREER Award 1741634, NSF\#1937599, Okawa Foundation Grant, and Amazon Research Award. 

 