\section{Broader Impact}\label{app: broader impact}

Relational deep learning broadens the applicability of graph machine learning to include relational databases. Whilst the blueprint is general, and can be applied to a wide variety of tasks, including potentially hazardous ones, we have taken steps to focus attention of potential positive use cases. Specifically, the beta version of \relbench considers two databases, Amazon products, and Stack Exchange, that are designed to highlight the usefulness of RDL for driving online commerce and online social networks. Future releases of \relbench will continue to expand the range of databases into domains we reasonably expect to be positive, such as biomedical data and sports fixtures. We hope these concrete steps ensure the adoption of RDL for purposes broadly beneficial to society.

Whilst we strongly believe the \relbench has all the ingredients needed to be a long term benchamrk for relational deep learning, there are also possibilities for improvement and extension. Two such possibilities include: (1) RDL at scale: currently our implementation must load the entire database into working memory during training. For very large datasets this is not viable. Instead, a custom batch sampler is needed that acesses the database via queries to sample specific entities and their pkey-fkey neighbors; (2) Fully inductive link-prediction: our current link-prediction implementation supports predicting links for test time pairs (\emph{head,tail}) where \emph{head} is potentially new (unseen during training) and \emph{tail} seen in the training data. Extending this formulation to be fully inductive (\ie, \emph{tail} unseen during training) is possible, but out of the scope of this work for now. 